---
title: Data Visualisation Using slidify and rCharts
author: Karthik Shivkumar
mode  : selfcontained
framework: impressjs
github:
  user: ramnathv
  repo: slidify
twitter:
  text: "Slidify with impress.js!"
--- .slide x:-1000 y:-1500

<q>Aren't you just **bored** with all those slides-based presentations?</q>

--- .slide x:0 y:-1500

<q>Don't you think that presentations given **in modern browsers** shouldn't **copy the limits** of 'classic' slide decks?</q>

--- .slide x:1000 y:-1500

<q>Would you like to **impress your audience** with **stunning visualization** of your talk?</q>

--- #title x:0 y:0 scale:4

<span class="try">then you should try</span>
# impress.js^*
<span class="footnote">^* no rhyme intended</span>

--- #its x:850 y:3000 rot:45 scale:5

 It's a **presentation tool** <br/>
inspired by the idea behind [prezi.com](http://prezi.com) <br/>
and based on the **power of CSS3 transforms and transitions** in modern browsers.

--- #big x:3500 y:2100 rot:180 scale:6

visualize your <b>big</b> <span class="thoughts">thoughts</span>

--- #tiny x:2825 y:2325 z:-3000 rot:300 scale:1

and **tiny** ideas

--- #ing x:3500 y:-850 rot:270 scale:6
by <b class="positioning">positioning</b>, <b class="rotating">rotating</b> and <b class="scaling">scaling</b> them on an infinite canvas

--- #imagination x:6700 y:-300 scale:6

the only **limit** is your <b class="imagination">imagination</b>

--- #source x:6300 y:2000 rot:20 scale:4

want to know more?

<q>[use the source](http://github.com/bartaz/impress.js), Luke</q>

--- #one-more-thing x:6000 y:4000 scale:2

one more thing...

--- #its-in-3d x:6200 y:4300 z:-100 rotx:-40 roty:-10 scale:2

<span class="have">have</span> <span class="you">you</span> <span class="noticed">noticed</span> <span class="its">it's</span> <span class="in">in</span> <b>3D<sup>*</sup></b>?

<span class="footnote">* beat that, prezi ;)</span>

--- #ChartIntro x:-1000 y:5000  scale:1
And now, the real cool stuff..

--- #Chart1 x:-1000 y:7000  scale:1
Let's start easy. Here's a simple multibar chart
```{r chart1, echo=FALSE, cache=TRUE, include=TRUE, warnings= FALSE, errors= FALSE, results='asis'}
library(rCharts)
library(reshape2)
library(ggplot2)
hair_eye_male <- subset(as.data.frame(HairEyeColor), Sex == "Male")
n1 <- nPlot(Freq ~ Hair, group = "Eye", data = hair_eye_male, type = "multiBarChart")
n1$set(width = 900, height = 600)
n1$show('inline', include_assets = TRUE, standalone = TRUE)
```


--- #Chart2 x:0 y:7000 z:-4000  scale:1
A versatile time series chart.... 
```{r chart2, echo=FALSE, cache=TRUE, include=TRUE, warning=FALSE, errors= FALSE, results='asis'}
ecm <- reshape2::melt(economics[,c('date', 'uempmed', 'psavert')], id = 'date')
a <- nPlot(value ~ date, group = 'variable', data = ecm, type = 'lineWithFocusChart')
a$xAxis( tickFormat="#!function(d) {return d3.time.format('%b %Y')(new Date( d * 86400000 ));}!#" )
a$x2Axis( tickFormat="#!function(d) {return d3.time.format('%Y')(new Date( d * 86400000 ));}!#" )
a$xAxis( NULL, replace = T)
# Print chart
a$set(width = 900, height = 600)
a$show('inline', include_assets = TRUE, standalone = TRUE)
```
Choose an area in the **base graph**

--- #Chart3 x:1500 y:7000 z:0  scale:1
A scatter plot..
```{r chart3, echo=FALSE, cache=TRUE, include=TRUE, warning=FALSE, errors= FALSE, results='asis'}
# Prepare data
a <- hPlot(Pulse ~ Height, data = MASS::survey, type = "bubble", title = "Bubble Size: Age", size = "Age", group = "Exer")
a$chart(zoomType = "xy")
a$exporting(enabled = T)

# Print chart
a$set(width = 900, height = 600)
a$show('inline', include_assets = TRUE, standalone = TRUE)
```
Psst! Try selecting an area...

--- #Chart4 x:2000 y:6000 z:-4000  scale:1
Here's a line chart
```{r chart4, echo=FALSE, cache=TRUE, include=TRUE, warning=FALSE, errors= FALSE, results='asis'}
a <- hPlot(disp ~ qsec, data = datasets::mtcars, type = "spline", title = "Disp and Fuel Eff.", group = "am")
a$chart(zoomType = "xy")
a$exporting(enabled = T)

# Print chart
a$set(width = 900, height = 600)
a$show('inline', include_assets = TRUE, standalone = TRUE)
```

--- #Chart5 x:3000 y:7500 z:0  scale:1
Okay, How about some pie?
```{r chart5, echo=FALSE, cache=TRUE, include=TRUE, warning=FALSE, errors= FALSE, results='asis'}
x <- data.frame(key = c("a", "b", "c"), value = c(1, 2, 3))
a <- hPlot(x = "key", y = "value", data = x, type = "pie", title)


# Print chart
a$set(width = 900, height = 600)
a$show('inline', include_assets = TRUE, standalone = TRUE)
```

--- #Chart6 x:3500 y:7000 z:-4000  scale:1
A different flavour?
```{r chart6, echo=FALSE, cache=TRUE, include=TRUE, warning=FALSE, errors= FALSE, results='asis'}
a <- nPlot(~ cyl, data = mtcars, type = 'pieChart')

# Print chart
a$set(width = 900, height = 600)
a$show('inline', include_assets = TRUE, standalone = TRUE)
```
Did you try the buttons on the top right yet?

--- #Chart7 x:4000 y:8000 z:-4500  scale:1
How about a donut?
```{r chart7, echo=FALSE, cache=TRUE, include=TRUE, warning=FALSE, errors= FALSE, results='asis'}
a <- nPlot(~ cyl, data = mtcars, type = 'pieChart')
a$chart(donut = TRUE)

# Print chart
a$set(width = 900, height = 600)
a$show('inline', include_assets = TRUE, standalone = TRUE)
```

--- #Chart8 x:5000 y:7000 z:-4000  scale:1
The dreaded stacked area chart.
```{r chart8, echo=FALSE, cache=TRUE, include=TRUE, warning=FALSE, errors= FALSE, results='asis'}
dat <- data.frame(t=rep(0:23,each=4),var=rep(LETTERS[1:4],4),val=round(runif(4*24,0,50)))
a <- nPlot(val ~ t, group =  'var', data = dat, type = 'stackedAreaChart', id = 'chart')

# Print chart
a$set(width = 900, height = 600)
a$show('inline', include_assets = TRUE, standalone = TRUE)
```


--- #Attribution x:4250 y:6000 z:-4000  scale:1
You can find My Github Page [here](https://github.com/karthikskumar/).
Find the source code for this presentation [here] (https://github.com/karthikskumar/karthikskumar.github.io).

This deck was built using [Slidify](http://www.slidify.org) and styled with [impress.js](http://github.com/bartaz/impress.js). Click [here](https://raw.github.com/ramnathv/slidify/gh-pages/samples/impressjs/index.Rmd) to view the source! 